\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-09-24 document/XSGRB_sample.tex
Moving table to separate file. Update for GRB100724A

	\LongTables

	\begin{deluxetable*}{@{\extracolsep{\fill}}lcccccclc@{}}
		%\tabletypesize{\scriptsize}
		%\rotate
		\tablecaption{The full sample of afterglows or hosts observed in the program.
			We here list the burst names and details of the spectroscopic observations. The
			exposure times and slit widths are given in the order UVB/VIS/NIR. The column
			$\Delta t$ shows the time after trigger when the spectroscopic observation was
			started. Mag$_\mathrm{acq}$ gives the approximate magnitude (typically in the
			$R$-band) of the afterglow in the acquisition image.
			\label{sample}}
		\tablewidth{0pt}
		\tablehead{
			\colhead{GRB} &  \colhead{Exptime} & \colhead{Slit width} & \colhead{Airmass} & \colhead{Seeing} & \colhead{$\Delta t$} & \colhead{Mag$_\mathrm{acq}$} & \colhead{Redshift} & \colhead{Ref}\\
			&  \colhead{(ks)}   & \colhead{(arcsec)} &   & \colhead{(arcsec)} & \colhead{(hr)}       &  & &  \\
		}
		\startdata
		090313$^1$ & 6.9/6.9/6.9     & 1.0/0.9/0.9 & 1.2--1.4  & 1.0  &    45  &  21.6  & 3.3736 & (1) \\
		090530$^1$ & 4.8/4.8/4.8     & 1.0/1.2/1.2 & 1.6--2.2  & 1.5  &    20  &  22    & 1.266 & (2) \\
		090809$^1$ & 7.2/7.2/7.2     & 1.0/0.9/0.9 & 1.2--1.1  & 0.9  &  10.2  &  21    & 2.737  & (2,3) \\
		090926$^1$ & 7.2/7.2/7.2     & 1.0/0.9/0.9 & 1.4--1.5  & 0.9  &    22  &  17.9  & 2.1062 & (4) \\
		091018     & 2.4/2.4/2.4     & 1.0/0.9/0.9 & 2.1--1.8  & 0.8  &   3.5  &  19.1  & 0.9710 & (5) \\  
		091127     & 6.0/6.0/6.0     & 1.0/0.9/0.9 & 1.1--1.2  & 1.0  &   101  &  21.2  & 0.490  & (6) \\
		100205A     & 10.8/10.8/10.8 & 1.0/0.9/0.9 & 1.9--1.8  & 1.0  &    71  &   --   &  --    & (2) \\
		100219A     &  4.8/4.8/4.8   & 1.0/0.9/0.9 & 1.3--1.1  & 0.7  &  12.5  &   23   & 4.667  & (7) \\
		100316B     &  2.4/2.4/2.4   & 1.0/0.9/0.9 & 2.0--2.4  & 0.7  &   0.7  &  18.2  & 1.18   & (2) \\
		100316D-1$^2$ &  7.2/7.2/7.2   & 1.0/0.9/0.9 & 1.2--1.5  & 1.0  &  12  &   --   & 0.059  & (8) \\
		100316D-2   &  2.4/2.4/2.4   & 1.0/0.9/0.9 & 1.2--1.2  & 1.0  &    58  &   --   & 0.059  & (8) \\
		100316D-3   &  2.4/2.4/2.4   & 1.0/0.9/0.9 & 1.2--1.2  & 0.8  &   192  &   --   & 0.059  & (8) \\
		100418A-1   &  4.8/4.8/4.8   & 1.0/0.9/0.9 & 1.6--1.3  & 0.7  &   8.4  &  18.1  & 0.6235 & (9) \\
		100418A-2   &  4.8/4.8/4.8   & 1.0/0.9/0.9 & 1.2--1.3  & 0.6  &    34  &   --   & 0.6235 & (9) \\
		100418A-3   &  4.8/4.8/4.8   & 1.0/0.9/0.9 & 1.2--1.4  & 0.7  &    58  &   --   & 0.6235 & (9) \\
		100424A$^3$ &  4.8/4.8/4.8   & 1.0/0.9/0.9 & 1.1--1.2  & 0.8  &   --   &   --   & 2.465  & (2) \\
		100425A     &  2.4/2.4/2.4   & 1.0/0.9/0.9 & 1.5--1.3  & 0.7  &   4.0  &  20.6  & 1.755  & (2,3) \\
		100621A     &  2.4/2.4/2.4   & 1.0/0.9/0.9 & 1.3--1.4  & 1.0  &   7.1  &   --   & 0.542  & (2) \\
		100625A$^3$ &  4.8/4.8/4.8   & 1.0/0.9/0.9 & 1.1--1.0  & 0.8  &    13  &   --   & 0.452  & (2) \\
		100724A$^4$ &  4.2/4.2/4.2   & 1.0/0.9/0.9 & 1.5--2.3  &      &   0.2  &   --   & 1.288  & (2) \\
		100728B$^5$ &  7.2/7.2/7.2   & 1.0/0.9/0.9 & 1.5--1.1  & 0.5  &    22  &   23   & 2.106  & (2) \\
		100814A-1$^4$ & 0.9/0.9/0.9  & 1.0/0.9/0.9 & 1.9--1.7  & 0.5  &   0.8  &   19   & 1.44   & (2) \\
		100814A-2   &  4.8/4.8/4.8   & 1.0/0.9/0.9 & 1.5--1.2  & 0.6  &   1.4  &   19   & 1.44   & (2) \\
		100814A-3   &  4.8/4.8/4.8   & 1.0/0.9/0.9 & 1.2--1.0  & 0.6  &   99   &   20   & 1.44   & (2) \\
		100816A$^6$ &  4.8/4.8/4.8   & 1.0/0.9/0.9 & 1.8--1.6  & 0.8  &   3.7  &   --   & 0.806  & (2) \\
		100901A     &  2.4/2.4/2.4   & 1.0/0.9/0.9 & 1.5--1.5  & 1.8  &   66   &   --   & 1.408  & (10) \\
		101219A     &  7.2/7.2/7.2   & 1.0/0.9/0.9 & 1.1--1.7  & 2.0  &   3.7  &   --   & 0.718  & (2) \\
		101219B-1   &  4.8/4.8/4.8   & 1.0/0.9/0.9 & 1.6--2.6  & 1.3  &  11.6  &   20   & 0.5519 & (11) \\
		101219B-2   &  7.2/7.2/7.2   & 1.0/0.9/0.9 & 1.2--2.0  & 0.8  &   394  &  22.7  & 0.5519 & (11) \\
		101219B-3   &  7.2/7.2/7.2   & 1.0/0.9/0.9 & 1.4--2.1  & 0.9  &   886  &   --   & 0.5519 & (11) \\
		110128A     &  7.2/7.2/7.2   & 1.0/0.9/0.9 & 2.0--1.6  & 0.9  &   5.5  &  22.5  & 2.339  & (2) \\
		110407A     &  9.6/9.6/9.6   & 1.0/0.9/0.9 & 1.4--1.3  & 2.0  &  12.4  &   23   &  --    & (2) \\
		110709B$^1,3$ &  7.2/7.2/7.2 & 1.0/0.9/0.9 & 1.6--1.1  & 1.0  &   --   &   --   &  --    & (2) \\
		110715A     &  0.6/0.6/0.6   & 1.0/0.9/0.9 & 1.1--1.1  & 1.7  &  12.3  &  18.5  & 0.82  & (2) \\
		%110721A     &  2.4/2.4/2.4   & 1.0/0.9/0.9 & 1.2--1.4  & 2.4  &        &        & 0.382  & (2) \\
		110808A     & 2.4/2.4/2.4    & 1.0/0.9/0.9 & 1.2--1.1  & 1.1  &   3.0  &  21.2  & 1.3488 & (2) \\
		110818A     & 4.8/4.8/4.8    & 1.0/0.9/0.9 & 1.3--1.3  & 1.0  &   6.2  &  22.3  & 3.36   & (2) \\
		111005A$^3$ & 1.2/1.2/1.2    & 1.0/0.9/0.9 & 1.3--1.3  & 0.7  &   --   &  --    & 0.013? & (2) \\
		111008A-1   & 8.8/8.8/8.4    & 1.0/0.9/0.9 & 1.1--1.0  & 1.2  &   8.5  &  21?   & 4.9898 & (12) \\
		111008A-2   & 8.0/8.0/7.2    & 1.0/0.9/0.9 & 1.3--1.0  & 1.0  &  20.1  &  22?   & 4.9898 & (12) \\
		111107A     & 4.8/4.8/4.8    & 1.0/0.9/0.9 & 1.8--1.5  & 0.7  &   5.3  &  21.5  & 2.893  & (2) \\
		111117A$^6$ & 4.8/4.8/4.8    & 1.0/0.9/0.9 & 1.5--1.4  & 0.6  &    38  &  --    & 1.3?   & (2) \\
		111123A-1   & 6.2/6.6/6.6    & 1.0/0.9/0.9 & 1.6--1.1  & 1.0  &  12.2  &  $>$24 & 3.1516 & (2) \\
		111123A-2$^3$ & 2.4/2.4/2.4  & 1.0/0.9/0.9 & 1.0--1.0  & 0.5  &   --   &  --    & 3.1516 & (2) \\
		111129A     & 3.6/3.6/3.6    & 1.0/0.9/0.9 & 1.6--2.1  & 1.7  &        &        &  --    & (2) \\
		111209A-1   & 4.8/4.8/4.8    & 1.0/0.9/0.9 & 1.1--1.2  & 0.8  &  17.7  &  20.1  & 0.677  & (13) \\
		111209A-2   & 9.6/9.6/9.6    & 1.0/0.9/0.9 & 1.2--2.0  & 0.8  &  497   &  23    & 0.677  & (13) \\
		111211A$^1$ & 2.4/2.4/2.4    & 1.0/0.9/0.9 & 1.4--1.6  & 0.6  &   31   &  19.5  & 0.478  & (2) \\
		111228A     & 2.4/2.4/2.4    & 1.0/0.9/0.9 & 1.4--1.4  & 0.9  &  15.9  &  20.1  & 0.716  & (2) \\
		120118B$^3$ & 3.6/3.6/3.6    & 1.0/0.9/0.9 & 1.1--1.0  & 1.0  &   --   &  --    & 2.943  & (2) \\
		120119A-1   & 2.4/2.4/2.4    & 1.0/0.9/0.9 & 1.1--1.1  & 0.6  &   1.4  &   17   & 1.728  & (2) \\
		120119A-2   & 1.2/1.2/1.2    & 1.0/0.9/0.9 & 1.8--1.9  & 0.6  &   4.5  &   20   & 1.728  & (2) \\
		120119A-3$^3$ & 4.8/4.8/4.8  & 1.0/0.9/0.6JH & 1.0--1.1  & 1.1 &   --   &   --   & 1.728  & (2) \\
		120211      &                &             &           &      &        &         & 2.346 & (2) \\
		120224A     & 2.4/2.4/2.4    & 1.0/0.9/0.9 & 1.7--2.1  & 1.4  &  19.8  &   22.3 &  --    & (2) \\
		120311A     & 2.4/2.4/2.4    & 1.0/0.9/0.9 & 1.6--1.4  & 0.6  &   3.7  &   21.6 &  --    & (2) \\
		120327A-1   & 2.4/2.4/2.4    & 1.0/0.9/0.9 & 1.6--1.4  & 0.5  &   2.1  &   18.8 & 2.815  & (14) \\
		120327A-2   & 4.2/4.2/4.2    & 1.0/0.9/0.9 & 1.0--1.1  & 1.0  &    29  &   22.5 & 2.815  & (14) \\
		120404A     & 9.6/9.6/9.6    & 1.0/0.9/0.9JH & 1.7--1.3 & 1.3 &  15.7  &   21.3 & 2.876  & (2) \\
		120422A-1   & 4.8/4.8/4.8    & 1.0/0.9/0.9 & 1.3--1.3  & 0.6  &  17.2  &   22.0 & 0.283  & (15) \\
		120422A-2   & 4.8/4.8/4.8    & 1.0/0.9/0.9 & 1.3--1.4  & 0.9  &  113   &   --   & 0.283  & (15) \\
		120422A-3   & 4.8/4.8/4.8    & 1.0/0.9/0.9 & 1.4--1.7  & 1.0  &  210   &   --   & 0.283  & (15) \\
		120422A-4   & 4.8/4.8/4.8    & 1.0/0.9/0.9JH & 1.3--1.4 & 0.6  & 449   &   --   & 0.283  & (15) \\
		120422A-5   & 4.8/4.8/4.8    & 1.0/0.9/0.9JH & 1.3--1.6 & 0.8  & 593   &   --   & 0.283  & (15) \\
		120422A-6   & 4.8/4.8/4.8    & 1.0/0.9/0.9JH & 1.7--2.4 & 2.5  & 882   &   --   & 0.283  & (15) \\
		120422A-7   & 4.8/4.8/4.8    & 1.0/0.9/0.9JH & 1.5--1.9 & 1.3  & 906   &   --   & 0.283  & (15) \\
		120712A     & 4.8/4.8/4.8    & 1.0/0.9/0.9   & 1.5--2.5 & 1.3  & 10.4  &   21.5 & 4.175  & (2) \\
		120714B     & 4.8/4.8/4.8    & 1.0/0.9/0.9JH & 1.5--1.2 & 1.2  &  7.8  &   22.1 & 0.398  & (2)\\
		120716A$^1$ & 3.6/3.6/3.6    & 1.0/0.9/0.9JH & 1.8--2.6 & 1.0  &  62   &   20.9 & 2.486  & (2) \\
		120722A$^2$ & 4.8/4.8/4.8    & 1.0/0.9/0.9   & 1.3--1.3 & 1.1  & 10.3  &   23.6 & 0.959  & (2) \\
		120805A$^2$ & 3.6/3.6/3.6    & 1.0/0.9/0.9JH & 1.3--1.7 & 0.9  & 218   &   --   & 2.8?   & (2) \\
		120815A     & 2.4/2.4/2.4    & 1.0/0.9/0.9   & 1.3--1.4 & 0.6  &  1.7  &   20   & 2.358  & (16) \\
		120909A     & 1.2/1.2/1.2    & 1.0/0.9/0.9   & 1.6--1.6 & 1.4  &  1.7  &   21   & 3.929  & (2) \\
		120923A     & 9.6/9.6/9.6    & 1.0/0.9/0.9JH & 1.2--1.4 & 1.0  & 18.5  &   --   & $\gtrsim8$ & (2) \\
		121024A     & 2.4/2.4/2.4    & 1.0/0.9/0.9   & 1.2--1.1 & 0.6  &  1.8  &   20   & 2.300  & (17) \\
		121027A     & 8.4/8.4/8.4    & 1.0/0.9/0.9   & 1.3--1.3 & 0.9  &  69   &  21.1  & 1.773  & (2) \\
		121201A     & 4.8/4.8/4.8    & 1.0/0.9/0.9JH & 1.1--1.1 & 0.9  & 12.9  &   23   & 3.385  & (2) \\
		121229A     & 4.8/4.8/4.8    & 1.0/0.9/0.9JH & 1.4--1.2 & 1.4  &  2.0  &  21.5  & 2.707  & (2) \\
		130131B$^3$ & 7.2/7.2/7.2    & 1.0/0.9/0.9JH & 1.3--1.6 & 0.8  &  --   &   --   & 2.539  & (2) \\
		130408A     & 1.2/1.2/1.2    & 1.0/0.9/0.9   & 1.0--1.0 & 1.0  &  1.9  &   20   & 3.758  & (2) \\
		130418A     & 1.2/1.2/1.2    & 1.0/0.9/0.9   & 1.4--1.3 & 1.3  &  4.6  &   18.5 & 1.218  & (2) \\
		130427A     & 1.2/1.2/1.2    & 1.0/0.9/0.9JH & 1.8--1.8 & 0.8  & 16.5  &   19   & 0.340  & (18) \\
		130427B     & 1.2/1.2/1.2    & 1.0/0.9/0.9JH & 1.2--1.0 & 0.8  & 20.3  &   22.7 & 2.78   &  (2) \\
		130603B$^6$ & 2.4/2.4/2.4    & 1.0/0.9/0.9   & 1.4--1.4 & 1.1  &  8.2  &   21.5 & 0.356  & (19) \\
		130606A     & 4.2/4.2/4.2    & 1.0/0.9/0.9JH & 1.7--1.9 & 1.1  &  7.1  &   19   & 5.91   & (20) \\
		130612A     & 1.2/1.2/1.2    & 1.0/0.9/0.9   & 1.3--1.3 & 1.4  &  1.1  &   21.5 & 2.006  & (2) \\
		130615A     & 1.2/1.2/1.2    & 1.0/0.9/0.9   & 2.1--2.2 & 1.0  &  0.8  &   21   & $~3$?  & (2) \\
		130701A     & 1.2/1.2/1.2    & 1.0/0.9/0.9JH & 2.0--2.0 & 1.6  &  5.5  &   19.9 & 1.155  & (2) \\
		\enddata
		\tablenotetext{1}{Not part of the statistical sample}
		\tablenotetext{2}{Spectrum dominated by light from the host galaxy}
		\tablenotetext{3}{Spectrum of the host galaxy taken long after the burst}
		\tablenotetext{4}{RRM observation}
		\tablenotetext{5}{ADC malfunction during observation}
		\tablenotetext{6}{Short burst}
		\tablerefs{
			(1) \citet{DeUgartePostigo2010}; (2) This work ; (3) Skuladottir (2010);
			(4) \citet{DElia2010}; (5) \citet{Wiersema2012}; (6) \citet{Vergani2011, Cobb2010}; 
			(7) \citet{Thone2013}; (8) \citet{Bufano2011} ; (9) \citet{DeUgartePostigo2011} ;
			(10) \citet{Hartoog2013}; (11) \citet{Sparre2011}; (12) \citet{Sparre2014};
			(13) \citet{Levan2014}; (14) \citet{DElia2014}; (15) \citet{Schulze2014};
			(16) \citet{Kruhler2013}; (17} \citet{Friis2015}
	\end{deluxetable*}
	%-------------------------END TABLE---------------------------------------

@@

	\subsection{GRB130606A (z = 5.913)}
	The data presented here also formed the basis of GCN \#
	14816\footnote{\url{http://gcn.gsfc.nasa.gov/gcn3/14816.gcn3}} and is published
	in \citet{Hartoog2015}.
	The observations consists of three 2x600sec visits starting 7.1 hr after the burst at fairly
	high airmass.
	We detect absorption features from a wide range of ions at z=5.913 
	as well as intervening absorption at $z=2.313, 2.521, 3.415, 4.6448, 4.6468, 4 and 4.6495$.

>>>>

	\input{tables/burst_overview.tex}

@@
